Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2018-09-13 supplement.tex
Add GC distribution plots

@@

>>>>

Fig.~\ref{fig:gc-content} shows the distributions of the GC content of the samples, while targeting different combinations of energies in this experiment. For completeness, we also report corresponding results for the analogous experiment from the main text. We observe that in addition to the target energies, also the feature $\GCb\%$ is narrowly defined by the multi-dimensional Boltzmann sampling strategy. In comparison, for uniform sampling and Boltzmann sampling at high weight $e^\beta$, where the \GCb\% is not controlled, we obtain much broader distributions.

@@

\begin{figure}
  \begin{center}
    {\sf \bfseries A}\includegraphicstop[width=0.45\textwidth]{Figs/Plots/PKB00211_PKB00239_0_GC_content}
    ~~~~~{\sf \bfseries B}
    \includegraphicstop[width=0.45\textwidth]{Figs/Plots/supp_3str_GC_content}
  \end{center}
  \caption{Distribution of the \GCb-content \GCb\% in the experiments of (A) Fig.~\ref{fig:energydist-pk} of the main text and (B) Suppl.~Fig.~\ref{fig:energydist}.}
  \label{fig:gc-content}
\end{figure}
